Exploring Alternative Routes Using Multipath TCP

### 2017-06-01 paper/presentation.tex
presentation: add forgotten presenter notes
presentation: title some figure slides

\newcommand{\TitledFigureSlide}[2]{
  \begin{frame}{#2}
    \begin{centering}
      \vfill
      \includegraphics[max width=\textwidth,max height=\textheight]{#1}
      \vfill
      \end{centering}
  \end{frame}
}

@@

\FigureSlide{figures/InternetSlide.pdf}{

@@

  \begin{itemize}
  \item Subflows are established with a three way handshake
  \item First subflow uses \texttt{MP\_CAPABLE} option
  \item Subsequent subflows use \texttt{MP\_JOIN} option
  \item Additional addresses may be advertised using \texttt{ADD\_ADDR} at any
    time
  \item Either side may create new subflows at any time
  \item Spec says nothing about when they should be created, left up to policy
  \item Kernel uses modular path manager interface for this
  \end{itemize}
  \note{

@@

\FigureSlide{figures/Concept.pdf}{
  \begin{itemize}
  \item Some terminology.
  \item Active opener - ``client''
  \item Passive opener - ``server''
  \item Intermediary - ``detour''
  \item This mechanism allows subflows to be created across (potentially
    multiple) detours
  \item (in addition to the main subflow directly from client to server)
  \end{itemize}
}

@@

\section{All Figures}
\TitledFigureSlide{figures/sym.pdf}{Throughput Comparison, Symmetric}
\TitledFigureSlide{figures/timegrid-sym.pdf}{Timelapse, Symmetric}

\TitledFigureSlide{figures/sym-lossy.pdf}{Throughput Comparison, Symmetric with Loss}
\TitledFigureSlide{figures/timegrid-sym-lossy.pdf}{Timelapse, Symmetric with Loss}

\TitledFigureSlide{figures/sym-delayed.pdf}{Throughput Comparison, Symmetric with Delay}
\TitledFigureSlide{figures/timegrid-sym-delayed.pdf}{Timelapse, Symmetric with Delay}

\TitledFigureSlide{figures/easy.pdf}{Throughput Comparison, Core-limited}
\TitledFigureSlide{figures/timegrid-easy.pdf}{Timelapse, Core-limited}

\TitledFigureSlide{figures/lossy.pdf}{Throughput Comparison, Core-limited with Loss}
\TitledFigureSlide{figures/timegrid-lossy.pdf}{Timelapse, Core-limited with Loss}

\TitledFigureSlide{figures/delayed.pdf}{Throughput Comparison, Core-limited with Delay}
\TitledFigureSlide{figures/timegrid-delayed.pdf}{Timelapse, Core-limited with Delay}

\TitledFigureSlide{figures/aws.pdf}{Throughput Comparison, AWS}
\TitledFigureSlide{figures/timegrid-aws.pdf}{Timelapse, AWS}

>>>>

\newcommand{\TitledFigureSlide}[3]{
  \begin{frame}{#2}
    \begin{centering}
      \vfill
      \includegraphics[max width=\textwidth,max height=\textheight]{#1}
      \vfill
      \end{centering}
      \note{#3}
  \end{frame}
}

@@

\TitledFigureSlide{figures/InternetSlide.pdf}{Internet Architecture}{

@@

  \begin{itemize}
  \item Subflows are established with a three way handshake
  \item First subflow uses \texttt{MP\_CAPABLE} option
  \item Subsequent subflows use \texttt{MP\_JOIN} option
  \item Additional addresses may be advertised using \texttt{ADD\_ADDR} at any
    time
  \item Either side may create new subflows at any time
  \end{itemize}
  \note{

    \begin{itemize}
    \item Normal 3WHS for subflow initiation
    \item First subflow contains MP CAPABLE, exchanges key material
    \item Subsequent subflows contain MP JOIN, plus HMAC to verify identities
    \item Either side may passively announce the existence of an address
    \item Spec says nothing about when they should be created, left up to policy
    \item Kernel uses modular path manager interface for this
    \end{itemize}

@@

\TitledFigureSlide{figures/Concept.pdf}{Concept Overview}{
  \begin{itemize}
  \item Some terminology.
  \item Active opener - ``client''
  \item Passive opener - ``server''
  \item Intermediary - ``detour''
  \item This mechanism allows subflows to be created across (potentially
    multiple) detours
  \item (in addition to the main subflow directly from client to server)
  \end{itemize}
}

@@

\section{All Figures}
\TitledFigureSlide{figures/sym.pdf}{Throughput Comparison, Symmetric}{}
\TitledFigureSlide{figures/timegrid-sym.pdf}{Timelapse, Symmetric}{}

\TitledFigureSlide{figures/sym-lossy.pdf}{Throughput Comparison, Symmetric with Loss}{}
\TitledFigureSlide{figures/timegrid-sym-lossy.pdf}{Timelapse, Symmetric with Loss}{}

\TitledFigureSlide{figures/sym-delayed.pdf}{Throughput Comparison, Symmetric with Delay}{}
\TitledFigureSlide{figures/timegrid-sym-delayed.pdf}{Timelapse, Symmetric with Delay}{}

\TitledFigureSlide{figures/easy.pdf}{Throughput Comparison, Core-limited}{}
\TitledFigureSlide{figures/timegrid-easy.pdf}{Timelapse, Core-limited}{}

\TitledFigureSlide{figures/lossy.pdf}{Throughput Comparison, Core-limited with Loss}{}
\TitledFigureSlide{figures/timegrid-lossy.pdf}{Timelapse, Core-limited with Loss}{}

\TitledFigureSlide{figures/delayed.pdf}{Throughput Comparison, Core-limited with Delay}{}
\TitledFigureSlide{figures/timegrid-delayed.pdf}{Timelapse, Core-limited with Delay}{}

\TitledFigureSlide{figures/aws.pdf}{Throughput Comparison, AWS}{}
\TitledFigureSlide{figures/timegrid-aws.pdf}{Timelapse, AWS}{}
